---
output:
  html_document:
    css: "styles.css"
    self_contained: false
---

```{r setup, warning = F, message = F, echo = F}
source(here::here('R/setup.R'))
load(file = here('data/expeddat.RData'))
yrsel <- 2025
tots <- expedsum_fun(expeddat, yrsel = c(2023:yrsel))
tots2024 <- expedsum_fun(expeddat, yrsel = 2024:yrsel)
```

Experiential education events are planned and facilitated by the Tampa Bay Estuary Program to increase environmental stewardship, well-being, and scientific literacy about key topics related to Tampa Bay ([Communication & Outreach Plan 2024](https://drive.google.com/file/d/1cPMlSIDgfinErzVVg6Vdy3Ycb_Xeodel/view){target="_parent"}). These events acknowledge that merging hands-on experience with guided education leads to a deeper understanding of key environmental topics. The target audience is the general public and anyone that has an interest in increasing knowledge about and stewardship of Tampa Bay.  

Since 2023, there have been `r tots['nevent']` experiential education events co-hosted with `r tots['ncorporatepartner']` bay-area partners.  Our goal for the 2024 to 2028 period is to engage over 600 participants. The goal to date is expressed below.

```{r, fig.height = 5, fig.width = 2.5}
expedtherm_plo(expeddat)
```

## `r yrsel` Year in Review 

```{r, out.width = '80%', fig.height = 12, fig.width = 14}
expeddat %>% 
  expedsum_fun(yrsel = yrsel) %>% 
  expedsum_plo(family = fml)
```

<script type="text/javascript" src="js/iframeResizer.contentWindow.min.js"></script>
