---
output:
  html_document:
    css: "styles.css"
---

```{r setup, warning = F, message = F, echo = F}
source(here::here('R/setup.R'))
load(file = here('data/tberfdat.RData'))
load(file = here('data/bmgdat.RData'))
load(file = here('data/dcgdat.RData'))
maxyr <- 2021
tberfsum <- grntsum_fun(tberfdat)
bmgsum <- grntsum_fun(bmgdat)
dcgsum <- grntsum_fun(dcgdat, rnd = 'k')
```

To date, TBERF has received `r tberfsum['total']` in funding and `r tberfsum['matching']` in matching funds to support `r tberfsum['n']` grants within the Tampa Bay watershed.

Funded by sales from of the Tampa Bay Estuary Specialty License Plate, also known as the "Tarpon Tag", Bay Mini-Grants provide competitive cash awards (up to \$5,000) to community organizations for projects that help restore and protect Tampa Bay. To achieve Program CCMP goals, specific Bay Mini-Grant priority actions are announced annually. Expanding the use of green infrastructure and understanding emerging contaminants have both been recent Bay Mini-Grant priorities. Since 2000, sales from the Tarpon Tag specialty license plate have collectively awarded `r bmgsum['total']` to more than `r bmgsum['n']` community-based restoration projects in the bay through TBEP's Bay Mini-Grant program.

Established during the COVID-19 pandemic, the Digital Challenge Grant program was created to provide safer-at-home income opportunities for digital content creators, science communicators, graphic designers, and educators. In its first year, `r dcgsum['n']` creators were awarded `r dcgsum['total']` in project funding.

### `r maxyr` FUNDING SUMMARY 

```{r}
grnt_tab(tberfdat, bmgdat, dcgdat, yrsel = maxyr, family = fml)
```

